### 2023-12-22 main.tex
''

@@

	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.

@@

 	Here we have only one term corresponding to $b=0$ in formula  \eqref{implicit-mass-function}.

@@

	Here we have two terms, the first corresponding to $b=0$  and the second corresponding to $b=1$ in formula  \eqref{implicit-mass-function}.

@@

 	Here the first term on the right-hand-side corresponds to $b=0$ and since $\bm{\tau}=(N,N)$ we obtain $1$. The second and the third term correspond to $b=1$. 

@@

	The fourth term corresponds to $b=2$.

@@

\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{1},a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{1}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{2}\}}\right\}+\ldots+

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots,a_{L-\ell}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{k}\}}\dt

@@

Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.  {Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}

@@

\subsubsection{Steady state}\label{appB}
By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary~\ref{Corollary-NESS-ABS}. Indeed we show here that 
$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary~\ref{Corollary-NESS-ABS}.
On a single site we have that 
\begin{equation}\label{S1-L1}
	\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
\end{equation}
thus,
\begin{equation}
	\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
	S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\dt
\end{equation}

		Considering 
			|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
		\end{equation} we obtain  

@@

			\Psi(\bm{\tau})=&\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
			{In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupation variables $a_{1},\ldots,a_{b}$. In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$, taking into account the Kronecker deltas.} Here, the notation

@@

			\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
		means that, {given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}. 

>>>>

{\color{blue}

@@

	\mu(\bm{\tau})=
	\sum_{m=0}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right]
\end{equation}}
%\begin{equation}\label{implicit-mass-function}
%	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{{1}},\ldots,a_{{b}}=1}^{N-1}{\color{black}
%	\mathbb{E}\left[\Bigg( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\Bigg) \Bigg(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{{k}}\}}\Bigg)\right]}\,.

@@

 	Here we have only one term corresponding to $m=2$ in formula  \eqref{implicit-mass-function}.

@@

	{\color{blue}Here in the last equality we have two terms: the first corresponding to $m=1$ (with $x_{1}=1$) and the second corresponding to $m=2$ in formula \eqref{implicit-mass-function}.}

@@

 	{\color{blue}Here in the last equality we have four terms: the first term corresponds to $m=0$, the second and the third term correspond to $m=1$ (with $x_{1}=1$ and $x_{1}=2$ respectively) and the fourth term corresponds to $m=2$ in formula \eqref{implicit-mass-function}. }

@@

@@

\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{x_{1}=1}^{L}\delta_{\tau_{x_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq x_{1}<x_{2}\leq L}\delta_{\tau_{x_{1}},N}\delta_{\tau_{x_{2}},N}\sum_{a_{1},a_{2}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}\right\}+\ldots+

@@

+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq x_{1}<\ldots<x_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{x_{k}},N}\right)\sum_{a_{1},\ldots,a_{L-\ell}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\dt

@@

{\color{blue}In the right-hand-side of the equation above the first addend is the product of the indicator of $\ell$ sites, since none of the empty sites of the configuration $\bm{\tau}$ has been considered. Similarly, the second addend is the product of the indicator of $\ell+1$ sites. Indeed, in addition to the $\ell$ occupied sites of $\bm{\tau}$ one empty site is in turn chosen and its hole is filled with all possible particles. In the next addends the idea is repeated with $2,3,...L-\ell$ empty sites in turn filled with all possible particles. We notice that the exponent of the factors (-1) is given by the number of holes that have been turned into particles. Then, we introduce an index $m\in \{\ell,\ell+1,\ldots,L\}$ that counts the number of correlated sites. For each $m$ we introduce the coordinates $1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L$. Then, we associate to to each of these $m$ one of the addend in \eqref{sum}. In particular, for $m=\ell$ we associate the first addend and we rewrite it as
		\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}=&\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{k=1}^{\ell}(1-\delta_{\tau_{x_{k}},N})\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)\nonumber
	\\	=&
		\sum_{1\leq x_{1}<\ldots<x_{\ell}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
	Similarly, the second addend in \eqref{sum} is associate to $m=\ell +1$ and it is rewritten as 
&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{x_{1}=1}^{L}\delta_{\tau_{x_{1}},N}\sum_{a_{1}=1}^{N-1}\mathbbm{1}_{\{Y_{x_{1}}
	a_{1}\}}\right\}
		\sum_{1\leq x_{1}<\ldots<x_{\ell+1}\leq L}\;\left(\prod_{x\notin \{x_{1},\ldots,x_{\ell+1}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{\ell+1}=1}^{N-1}\left(\prod_{k=1}^{\ell}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k},N}}\right)\left(\prod_{k=1}^{\ell+1}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}\right)
	The idea goes on for $m=\ell+2,\ldots L$ and we obtain that 
\sum_{m=\ell}^{L}\;\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=b_{k}\}}
The above sum can be extended from $m=0$ since all the terms before $m=0,\ldots,\ell-1$ are vanishing. 
Finally, by taking the expectation with respect to the steady state distribution we obtain \eqref{implicit-mass-function}.}  %{Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.} }

@@

\subsubsection{Steady state}\label{appB}
By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary~\ref{Corollary-NESS-ABS}. Indeed we show here that 
$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary~\ref{Corollary-NESS-ABS}.
On a single site we have that 
\begin{equation}\label{S1-L1}
	\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
thus,
	\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
By taking the tensor product over the chain we obtain 
	S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\dt
	By inserting the resolution of identity $\sum_{\bm{\sigma}\in \Omega^{'}} |\bm{\sigma}\rangle\langle\bm{\sigma}|$ we have that 
{\color{blue}
		\Psi(\bm{\tau})=\langle \bm{\tau}|\Psi\rangle=\langle \bm{\tau}|S^{-1}_{1}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{-1}|\bm{\sigma}\rangle \langle \bm{\sigma}|\Psi^{'}\rangle\dt
		%=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
	%Considering 
	%|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle\co
	%\end{equation} and 
	Using \eqref{Tensor-S1} we obtain 

@@

			\Psi(\bm{\tau})=&\sum_{m=0}^{L}\sum_{1\leq x_{1}<x_{2}<\ldots<x_{m}\leq L}\left(\prod_{x\notin\{x_{1},\ldots,x_{m}\}}\delta_{\tau_{x_{k}},N}\right)\sum_{b_{1},\ldots,b_{m}=1}^{N-1}\left(\prod_{k=1}^{m}\delta_{\tau_{x_{k}},b_{k}}-\delta_{\tau_{x_{k}},N}\right)\nonumber\\
			\times &			
			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
			%=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
			In the second equality we have rewritten the product by introducing the summation over $m$, the coordinates $x_{1},\ldots,x_{m}$ and the occupation variables $b_{1},\ldots,b_{m}$. Here, the notation

@@

		%	\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
			\Psi^{'}(N,\ldots,N,\underset{\uparrow}{b_{1}}_{x_{1}},N,\ldots,N,\underset{\uparrow}{b_{m}}_{x_{m}},N,\ldots,N)
		indicates that in positions $x_{1},\ldots,x_{m}$ we have particles of species $b_{1},\ldots,b_{m}$ and we have holes $N$ in all other positions.} %{given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$}☺ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). }  One can check that equation \eqref{implicit-PSI-PSIp} is indeed formula \eqref{implicit-mass-function} of Corollary~\ref{Corollary-NESS-ABS}. 
